\emph{On Logics Extended with Embedding-Closed Quantifiers}

### 2020-11-22 paper.tex
Add open questions

Note that a structure $\mathfrak{A}$ is homogeneous (quasi-homogeneous) if and
only if for all tuples $\overline{a}$ and $\overline{b}$ of the same atomic type
there is an automorphism (embedding) of $\mathfrak{A}$ taking
$\overline{a}$ to $\overline{b}$.
A routine back-and-forth argument shows that every countable quasi-homogeneous
structure is homogeneous.
Let $\mathfrak{R} = (R\setminus\{r\},\leq)$ be the usual ordering of real
numbers with some number $r$ removed.
This ``punctured'' real line is an example of a structure that is
quasi-homogeneous but not homogeneous.

@@

>>>>

Note that a structure $\mathfrak{A}$ is homogeneous (quasi-homogeneous) if and
only if for all tuples $\overline{a}$ and $\overline{b}$ of the same atomic type
there is an automorphism (embedding) of $\mathfrak{A}$ taking
$\overline{a}$ to $\overline{b}$.
A routine back-and-forth argument shows that every countable quasi-homogeneous
structure is homogeneous.
Let $\mathfrak{R} = (\mathbb{R} \setminus \{r\}, \leq)$ be the usual ordering of real
numbers with some number $r$ removed.
This ``punctured'' real line is an example of a structure that is
quasi-homogeneous but not homogeneous.

@@

\section{Open questions}
The notion of quasi-homogeneity introduced in this article does not seem to
appear in the literature.
Studying it in more depth could be one possible direction for the further 
research since at the moment our knowledge about it is quite limited.
For instance, we know that homogeneity and quasi-homogeneity coincide over 
countable structures
but how much they really differ over uncountable structures is a question 
that we leave open.

We also leave open the question asked by the referee about a
converse to Theorems \ref{finite} and \ref{infinite}.
Given a chain of structures, does having every formula of
$\mathcal{L}_{\infty \omega}(\mathcal{Q}_{\emb})$
eventually equivalent to some fixed quantifier-free formula in this chain 
imply that it eventually consists only of structures that are interpretations
of quasi-homogeneous structures for some fixed interpretation?
